Developing ShinyMICE

### 2020-01-13 2.ResearchReport/2.Presentation/Presentation_Hanne.Rmd
clean-up research report folder and edit readme

---
title: "Developing ShinyMICE"
subtitle: "A Note on Convergence Diagnostics for Multiple Imputation Algorithms"
author: "Hanne Oberman"
date: "December 16, 2019"
output: 
    ioslides_presentation:
        logo: figures/shinymice.png
        transition: 0
        smaller: TRUE
bibliography: ShinyMICE.bib

---

```{r setup, include=FALSE}
library("mice")
library("magrittr")
library("DT")
library("plotly")
library("dplyr")
library("ggplot2")
library("ggpubr")

@@

<!-- ## Disclaimer -->

@@

## Multiple imputation
<br><br>

@@

## Algorithmic convergence
<center>
<img src="figures/non-conv.png" alt="HTML5 Icon" width = 77%>
<br>

@@

## Results: simulation diagnostics
<center>
<img src="figures/results_sim.png" alt="HTML5 Icon" width = 100%>
<br>

@@

## Results: convergence diagnostics
<center>
<img src="figures/results_conv.png" alt="HTML5 Icon" width = 100%>
<br>

@@

## Results 
<center>
<img src="figures/results_sim_conv.png" alt="HTML5 Icon" width = 100%>
<br>

@@

## Discussion
<center>
<img src="figures/shinymice.png" alt="HTML5 Icon" width = 71%>
</center>

@@

## Impression of ShinyMICE
<center>
<br>

@@

## Equations $\widehat{R}$
\[\begin{align}
B&=\frac{T}{M-1} \sum_{m=1}^{M}\left(\bar{\theta}^{(\cdot m)}-\bar{\theta}^{(\cdot \cdot)}\right)^{2}, \quad \text{where} \quad \bar{\theta}^{(\cdot m)}=\frac{1}{T} \sum_{t=1}^{T} \theta^{(t m)}, \\
&\quad \text{ and } \quad \bar{\theta}^{(\cdot \cdot)}=\frac{1}{M} \sum_{m=1}^{M} \bar{\theta}^{(\cdot m)} \\
W&=\frac{1}{M} \sum_{m=1}^{M} s_{j}^{2},  \quad \text{where} \quad s_{m}^{2}=\frac{1}{T-1} \sum_{t=1}^{T}\left(\theta^{(t m)}-\bar{\theta}^{(\cdot m)}\right)^{2}  \\

\widehat{R}&=\sqrt{\frac{\widehat{\operatorname{var}}^{+}(\theta | y)}{W}},
\quad \text{where} \quad \widehat{\operatorname{var}}^{+}(\theta | y)=\frac{N-1}{N} W+\frac{1}{N} B.
\end{align}\]

>>>>

---
title: "Developing ShinyMICE"
subtitle: "A Note on Convergence Diagnostics for Multiple Imputation Algorithms"
author: "Hanne Oberman, December 16, 2019"
date: "Supervisors: Stef van Buuren and Gerko Vink | Mentor: Daniela Cianci"
output: 
    ioslides_presentation:
        logo: figures/shinymice.png
        transition: 0
        smaller: TRUE
bibliography: ShinyMICE.bib
nocite: | 
  @buur18, @R, @mice, @shiny, @veht19
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library("mice")
library("magrittr")
library("DT")
library("plotly")
library("dplyr")
library("ggplot2")
library("ggpubr")

@@

<style>
div.footnotes {
  position: absolute;
  bottom: 0;
  margin-bottom: 10px;
  width: 80%;
  font-size: 0.6em;
}
</style>

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>

<script>
  $(document).ready(function() {
    $('slide:not(.backdrop):not(.title-slide)').append('<div class=\"footnotes\">');

    $('footnote').each(function(index) {
      var text  = $(this).html();
      var fnNum = (index+1).toString().sup();
      $(this).html(text + fnNum);

      var footnote   = fnNum + ': ' + $(this).attr('content') + '<br/>';
      var oldContent = $(this).parents('slide').children('div.footnotes').html();
      var newContent = oldContent + footnote;
      $(this).parents('slide').children('div.footnotes').html(newContent);
    });
  });
</script>
<!-- ## Disclaimer -->

@@

## Multiple imputation <footnote content="Figure adapted from van Buuren (2018)"></footnote>

<br><br>

@@

## Algorithmic convergence <footnote content="Figure adapted from van Buuren (2018)"></footnote>
<center>
<img src="figures/non-conv.png" alt="HTML5 Icon" width = 77%>
<br>

@@

## Results: simulation diagnostics <footnote content="Results obtained using R (2019)"></footnote>
<center>
<img src="figures/results_sim.png" alt="HTML5 Icon" width = 100%>
<br>

@@

## Results: convergence diagnostics <footnote content="Results obtained using R (2019)"></footnote>
<center>
<img src="figures/results_conv.png" alt="HTML5 Icon" width = 100%>
<br>

@@

## Results <footnote content="Results obtained using R (2019)"></footnote>
<center>
<img src="figures/results_sim_conv.png" alt="HTML5 Icon" width = 100%>
<br>

@@

## Discussion <footnote content="Figure adapted from mice (2014) and Shiny (2017)"></footnote>
<center>
<img src="figures/shinymice.png" alt="HTML5 Icon" width = 71%>
</center>

@@

## Impression of ShinyMICE <footnote content="Figure adapted from mice (2014) and Shiny (2017)"></footnote>
<center>
<br>

@@

## Equations $\widehat{R}$ <footnote content="Adapted from Vehtari et al. (2019)"></footnote>
\[\begin{align}
B&=\frac{T}{M-1} \sum_{m=1}^{M}\left(\bar{\theta}^{(\cdot m)}-\bar{\theta}^{(\cdot \cdot)}\right)^{2}, \quad \text{where} \quad \bar{\theta}^{(\cdot m)}=\frac{1}{T} \sum_{t=1}^{T} \theta^{(t m)}, \\
&\quad \text{ and } \quad \bar{\theta}^{(\cdot \cdot)}=\frac{1}{M} \sum_{m=1}^{M} \bar{\theta}^{(\cdot m)} \\
W&=\frac{1}{M} \sum_{m=1}^{M} s_{j}^{2},  \quad \text{where} \quad s_{m}^{2}=\frac{1}{T-1} \sum_{t=1}^{T}\left(\theta^{(t m)}-\bar{\theta}^{(\cdot m)}\right)^{2}  \\
\widehat{R}&=\sqrt{\frac{\widehat{\operatorname{var}}^{+}(\theta | y)}{W}},
\quad \text{where} \quad \widehat{\operatorname{var}}^{+}(\theta | y)=\frac{N-1}{N} W+\frac{1}{N} B.
\end{align}\]
